---
title: "Viewership Analysis of *Better Call Saul*"
author: "Viktor Sas (465692)"
date: "2025-05-16"
output: html_document
---
# **_Better Call Saul_**: A Brief Introduction

**_Better Call Saul_** is an American television drama series created by **Vince Gilligan and Peter Gould**. It is a prequel to the critically acclaimed series Breaking Bad and follows the story of Jimmy McGill, a small-time lawyer slowly transforming into the morally flexible Saul Goodman.

**Premiering in 2015** on AMC, the **show ran for 6 seasons** and received critical praise for its writing, acting, and cinematography.


# Show Logo

![](https://en.wikipedia.org/wiki/File:Better_Call_Saul_logo.svg)
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(tidyr)
library(scales)
```

```{r data}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
viewership_data <- data.frame(
  Season = rep(1:6, times = c(10,10,10,10,10,13)),
  Episode = c(1:10, 1:10, 1:10, 1:10, 1:10, 1:13),
  Viewers = c(
    6.88, 3.42, 3.23, 2.87, 2.71, 2.57, 2.67, 2.87, 2.38, 2.53,
    2.57, 2.23, 2.20, 2.20, 1.99, 2.11, 2.03, 1.93, 2.06, 2.26,
    1.81, 1.46, 1.52, 1.56, 1.76, 1.72, 1.65, 1.63, 1.47, 1.85,
    1.77, 1.55, 1.51, 1.53, 1.53, 1.40, 1.35, 1.37, 1.35, 1.53,
    1.60, 1.06, 1.18, 1.22, 1.45, 1.40, 1.30, 1.42, 1.51, 1.59,
    1.42, 1.16, 1.16, 1.16, 1.22, 1.13, 1.19, 1.16, 1.22, 1.20, 1.34, 1.32, 1.80
  )
)
```

```{r summary}
viewership_summary <- viewership_data %>%
  group_by(Season) %>%
  summarise(
    Min = min(Viewers),
    Max = max(Viewers),
    Mean = mean(Viewers),
    Median = median(Viewers),
    Episodes = n()
  )

viewership_summary

```

```{r viewership over time}
ggplot(viewership_data, aes(x = Episode, y = Viewers, group = Season, color = factor(Season))) +
  geom_line(size = 1) +
  geom_point() +
  labs(
    title = "Viewership Over Episodes by Season",
    x = "Episode Number",
    y = "Viewers (in millions)",
    color = "Season"
  ) +
  theme_minimal()


```


```{r viewership over time}
# Create a sequential episode number across all seasons
viewership_data <- viewership_data %>%
  mutate(Episode_Sequential = row_number(),
         Season = as.factor(Season))  # convert Season to factor for coloring

# Plot
ggplot(viewership_data, aes(x = Episode_Sequential, y = Viewers, fill = Season)) +
  geom_bar(stat = "identity", color = "black") +
  scale_fill_brewer(palette = "Set2") +
  labs(
    title = "Better Call Saul Viewership by Episode (Sequential)",
    x = "Episode Number (All Seasons)",
    y = "Viewers (in millions)",
    fill = "Season"
  ) +
  theme_minimal(base_size = 14)



```
